A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
tdm

All previous methods for analyzing \KT\ data involve some sort of
``correction'' or ``de-trending'' step based on measurements of the pointing
of the spacecraft \citep{Vanderburg:2014, Aigrain:2015, Crossfield:2015}.
In our analysis, we don't do any further preprocessing of the light curves
because, as we describe in the next \sectionname, we fit raw photometric light
curves with a model that includes both the trends and the transit signal.

@@

Ground-based transit surveys have experienced false-positive rates
well over 50~percent.  For example, \citet{Latham:2009} reported eight
eclipsing binaries and one transiting planet among the sample of
transit candidates in one field of the Hungarian Automated Telescope
Network transit search.  In fact, the follow-up process to try to rule
out such astrophysical false positives is a large portion of the
effort that goes into a transit survey
\citep[e.g.,][]{Odonovan:2006,Almenara:2009,Poleski:2010}.

@@

A quick \emph{a priori} estimate of the background blended eclipsing
binary rate serves as a good sanity check.  A query to the TRILEGAL
(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
line-of-sight simulation software reveals that the typical density of
field stars along the line of sight to the C1 field is about
$7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
0.16 that a background star might be blended within a 8\,arcsec radius
(two pixels) from a target star.  Allowing that $\sim$10\% of stars
might host close binary companions within the period range accessible
by this survey, this gives a probability of 0.016 that a blended
binary star might be chance-aligned within two pixels of any given
target star.  Noting that the average number of planets per star with
periods less than 30 days is about 0.25 \citep{Fressin:2013}, we can
roughly estimate that we expect $<$10\% of our candidates to be caused
by nearby contaminating EBs.  This estimate suggests that such
astrophysical false positives should be rare in our sample, consistent
with our detection of 2/36 candidates with clear centroid offsets.

@@

The remaining signals are caused by EBs with visible secondary eclipses.
In most cases, the search reports the secondary eclipse as a candidate and in
a few very high signal-to-noise cases, the period reported by the pipeline is
incorrect and multiple candidates correspond to the same transit.
It is important to note, however, that the choices made in the search were
heuristically tuned to find planets, not binaries, so our results are not
complete or exhaustive, especially at short orbital periods.
There are other methods specifically tuned to find EBs in \KT\
\citep[such as][]{Armstrong:2014, Armstrong:2015} and these catalogs contain
our full sample of EBs and more.

@@

This research made use of the NASA \project{Astrophysics Data System} and the
NASA Exoplanet Archive.
The Archive is operated by the California Institute of Technology, under
contract with NASA under the Exoplanet Exploration Program.
This \paper\ includes data collected by the \kepler\ mission. Funding for the
\kepler\ mission is provided by the NASA Science Mission directorate.
We are grateful to the entire \kepler\ team, past and present.
Their tireless efforts were all essential to the tremendous success of the mission
and the successes of \KT, present and future.
These data were obtained from the Mikulski Archive for Space Telescopes
(MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST is provided by the NASA Office of Space Science via grant
NNX13AC07G and by other grants and contracts.

{\it Facilities:} \facility{Kepler}, \facility{K2}

>>>>

All previous methods for analyzing \KT\ data involve some sort of
``correction'' or ``de-trending'' step based on measurements of the pointing
of the spacecraft \citep{Vanderburg:2014, Aigrain:2015, Crossfield:2015}.
In our analysis, we do not do any further preprocessing of the light curves
because, as we describe in the next \sectionname, we fit raw photometric light
curves with a model that includes both the trends and the transit signal.

@@

Ground-based transit surveys have experienced false-positive rates
well over 50\%.  For example, \citet{Latham:2009} reported eight
eclipsing binaries and one transiting planet among the sample of
transit candidates in one field of the Hungarian Automated Telescope
Network transit search.  In fact, the follow-up process to try to rule
out such astrophysical false positives is a large portion of the
effort that goes into a transit survey
\citep[e.g.,][]{Odonovan:2006,Almenara:2009,Poleski:2010}.

@@

A quick \emph{a priori} estimate of the background blended ecipsing
binary rate serves as a good sanity check.  A query to the TRILEGAL
(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
line-of-sight simulation software reveals that the typical density of
field stars along the line of sight to the C1 field is about
$7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
0.16 that a background star might be blended within a 8\,arcsec radius
(two pixels) from a target star.  Allowing that $\sim$10\% of stars
might host close binary companions within the period range accessible
by this survey, this gives a probability of 0.016 that a blended
binary star might be chance-aligned within two pixels of any given
target star.  Noting that the average number of planets per star with
periods less than 30 days is about 0.25 \citep{Fressin:2013}, we can
roughly estimate that we expect $<$10\% of our candidates to be caused
by nearby contaminating EBs.  This estimate suggests that such
astrophsycial false positives should be rare in our sample, consistent
with our detection of 2/36 candidates with clear centroid offsets.

@@

The remaining signals are caused by eclipsing binaries (EBs) with visible
secondary eclipses.
In most cases, the search reports the secondary eclipse as a candidate and in
a few very high signal-to-noise cases, the period reported by the pipeline is
incorrect and multiple candidates correspond to the same transit.
It is important to note, however, that the choices made in the search were
heuristically tuned to find planets, not binaries, so our results are not
complete or exhaustive, especially at short orbital periods.
There are other methods specifically tuned to find EBs in \KT\
\citep[such as][]{Armstrong:2014, Armstrong:2015} and these catalogs contain
our full sample of EBs and more.

@@

This research made use of the NASA \project{Astrophysics Data System} and the
NASA Exoplanet Archive.
The Archive is operated by the California Institute of Technology, under
contract with NASA under the Exoplanet Exploration Program.
This \paper\ includes data collected by the \kepler\ mission. Funding for the
\kepler\ mission is provided by the NASA Science Mission directorate.
These data were obtained from the Mikulski Archive for Space Telescopes
(MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST is provided by the NASA Office of Space Science via grant
NNX13AC07G and by other grants and contracts.

{\it Facilities:} \facility{Kepler}
